Model LF

### 2022-10-13 max_dp endogen stød.Rmd
Commit

 sens3_low = TIMESERIES(sens3_low+1 ,START=c(2016,1),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

>>>>

 sens3_low = TIMESERIES(sens3_low+1 ,START=c(2016,1),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)
```
